Problems from William Waterhouse's\\ \textit{Introduction to Affine Group Schemes}\vspace{-1ex}

### 2019-01-04 Reading Notes/reading_notes.tex
testing
Tweak styles and add some content

\usepackage{xcolor, amsmath, amsfonts, amssymb, graphicx, color, fancyhdr, lipsum, scalerel, stackengine, mathrsfs, tikz-cd, mdframed, enumitem}
\usepackage[amsthm]{ntheorem}
\usepackage[mathscr]{euscript}
%set margins
\usepackage[
top    = 1.0in,
bottom = 1.0in,
left   = 1.0in,
right  = 1.0in]{geometry}

%header stuff
\setlength{\headsep}{24pt}  % space between header and text
\pagestyle{fancy}     % set pagestyle for document
\lhead{ Problems from our reading course } % put text in header (left side)
\rhead{Nico Courts} % put text in header (right side)
\cfoot{\it p. \thepage}
\setlength{\headheight}{15pt}
\allowdisplaybreaks

@@

%socle
%restriction
\DeclareMathOperator{\Soc}{Soc}

@@

\newtheorem{lem}{Lemma}[subsection]
\newtheorem{thm}[lem]{Theorem}
\newtheorem{pro}[lem]{Problem}

\setenumerate[0]{label=(\alph*)}

%New environments for problem solving
\newenvironment{prob}{\par\smallskip
	\noindent\begin{mdframed}\small \begin{pro}}{\end{pro}\end{mdframed}\medskip}
\newenvironment{sol}{\noindent \textbf{Solution.} \,}{\\\hspace*{\fill}$\square$\medskip}

%\onehalfspacing
\begin{document}
%make the title page
\title{ Notes and Problems from My Research\vspace{-1ex}}
\author{Nico Courts}
\date{}
\maketitle

@@

\section{Winter 2019}
\subsection{Preparation: Waterhouse and G\"ortz \& Weddhorn}
Problems I worked from Waterhouse can be found in the appropriate file.

>>>>

\usepackage{xcolor, amsmath, amsfonts, amssymb, graphicx, color, fancyhdr, lipsum, scalerel, stackengine, mathrsfs, tikz-cd, mdframed, enumitem, framed, adjustbox}
\usepackage[framed,thmmarks]{ntheorem}
\usepackage[mathscr]{euscript}

%set up theorem/definition/etc envs
%Problems will be created using their own counter and style
\theoreminframepreskip{0pt}
\theoreminframepostskip{0pt}
\newframedtheorem{prob}{Problem}[section]

%solution template
\theoremstyle{nonumberbreak}
\theoremindent0.5cm
\theorembodyfont{\upshape}
\theoremseparator{:}
\theoremsymbol{\ensuremath\spadesuit}
\newtheorem{sol}{Solution}

%Theorems, Lemmas, and Corollaries
\theoremstyle{changebreak}
\theoremseparator{}
\theoremsymbol{}
\theoremindent0.5cm
\theoremheaderfont{\bfseries} 
\newtheorem{thm}{Theorem}[subsection]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}

%Create a new env that references a theorem and creates a 'primed' version
%Note this can be used recursively to get double, triple, etc primes
\newenvironment{thm-prime}[1]
  {\renewcommand{\thethm}{\ref{#1}$'$}%
   \addtocounter{thm}{-1}%
   \begin{thm}}
  {\end{thm}}

\setlength\fboxsep{15pt}

%Shade definitions
\theoremindent0cm
\theoremheaderfont{\normalfont\bfseries} 
\def\theoremframecommand{\colorbox[rgb]{.9,.9,1}}
\newshadedtheorem{defn}[thm]{Definition}

%Man, that's really good! Let's use the same thing for definitons.
\newenvironment{def-prime}[1]
  {\renewcommand{\thethm}{\ref{#1}$'$}%
   \addtocounter{thm}{-1}%
   \begin{def}}
  {\end{def}}

%proofs
\theoremstyle{nonumberbreak}
\theoremindent1cm
\theoremheaderfont{\sc}
\theoremseparator{}
\theoremsymbol{\ensuremath\spadesuit}
\newtheorem{prf}{Proof}

\usepackage{fullpage}
%set margins
%\usepackage[
%top    = 1.0in,
%bottom = 1.0in,
%left   = 1.0in,
%right  = 1.0in]{geometry}

%header stuff
\setlength{\headsep}{24pt}  % space between header and text
\pagestyle{fancy}     % set pagestyle for document
\lhead{Notes on Affine Group Schemes and Their Representations} % put text in header (left side)
\rhead{Nico Courts} % put text in header (right side)
\cfoot{\itshape p. \thepage}
\setlength{\headheight}{15pt}
\allowdisplaybreaks

@@

%socle
\DeclareMathOperator{\Soc}{Soc}

%rank
\DeclareMathOperator{\rank}{rank}

@@

% Enumerate will automatically use letters (e.g. part a,b,c,...)
\setenumerate[0]{label=(\alph*)}

\begin{document}
%make the title page
\title{Notes and Problems from My Research\vspace{-1ex}}
\author{Nico Courts}
\date{}
\maketitle

@@

\section{Winter 2019}
This is my first official quarter as Julia's student!! 
\subsection{Preparation, Waterhouse, and G\"ortz \& Weddhorn}
To give a sense of direction, Julia recommended that I take a look at the following regularity theorem:
\begin{thm}[Smoothness Theorem]\label{smooth}
	Let $G$ be an algebraic affine group scheme over a field $k$. Then $k[G]\otimes \bar k$ is reduced if and
	only if $\dim G = \rank \Omega_{k[G]}$.
\end{thm}
I have quite a bit of information to process before this, so I will get started!
\begin{defn}[Closed Embedding]
	If $G$ and $H$ are affine group schemes represented by $A$ and $B$, respectively and
	if $\psi:H\to G$ is a homomorphism of affine group schemes (locally a group homomorphism)
	then if the corresponding algebra map $A\to B$ is surjective, then $\psi$ is called
	a \textbf{closed embedding.}
\end{defn}

As its name suggests, this means that $\psi$ is an isomorphism onto a \textbf{closed subgroup}
$H'$ of $G$. This is, in fact, a definition of this property. One can also think about 
it in the following ways: a group scheme $H$ is closed in $G$ if
\begin{itemize}
	\item $H$ is defined by the relations imposed by $G$ plus some additional ones.
	\item $H=V(I)$ for some ideal $I\subset k[G]$. 
\end{itemize}
Thinking back to our algebraic geometry, these are not too hard to see as equivalent. 
For instance, there is a closed embedding of $\mu_n$ in $G_m$ (simply adding in $x^n-1$)
and of $SL_n$ in $GL_n$ (adding $\det = 1$).

\subsubsection{Hopf Ideals}
One problem with the above characterization that one cannot choose $I$ arbitrarily and end
up with a group scheme. This is equivalent to arbitrarily adding relations to a group, which is
not always guaranteed to work out well (think adding $\det = 2$ to $GL_n$).

Actually, we can exactly categorize the closed embeddings of subgroups in $G$ by considering certain
ideals of the algebra $A$ which represents it. 
\begin{defn}
	Let $A$ be an algebra and $I\lhd A$. Then if 
	\begin{itemize}
		\item $\Delta(I)$ goes to zero under the map $A\otimes A\to A/I\otimes A/I$,
		\item $S(I)\subseteq I$
		\item $\epsilon(I)=0$
	\end{itemize}
	then $I$ is called a \textbf{Hopf Ideal of $A$.}
\end{defn}

### 2019-01-04 Waterhouse Problems/waterhouse_problems.tex
Tweak styles and add some content

\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}

@@

\begin{prob}{}

\end{prob}
\begin{sol}
	a
\end{sol}

\begin{prob}{}

\end{prob}
\begin{sol}
	a
\end{sol}

>>>>

\newtheorem{lem}{Lemma}[section]
\newtheorem{thm}[lem]{Theorem}
\newtheorem{defn}[lem]{Definition}

@@

\section{Examples}
\begin{defn}[Closed Embedding]
	If $G$ and $H$ are affine group schemes represented by $A$ and $B$, respectively and
	if $\psi:H\to G$ is a homomorphism of affine group schemes (locally a group homomorphism)
	then if the corresponding algebra map $A\to B$ is surjective, then $\psi$ is called
	a \textbf{closed embedding.}
\end{defn}
